Manuscript figures

### 2024-04-29 02a_manuscript_plots.Rmd
restructure scripts

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(lubridate)
library(tidytext)
library(ggpattern)
library(ggpubr)
library(ggh4x)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(lubridate)
library(tidytext)
library(ggpattern)
library(ggpubr)
library(ggh4x)
```
## Get scores

```{r}
source('00_get_scores.R')
```

@@

## Inventory

```{r}

# How many models?
model_meta |>
  mutate(tw = str_detect(variable, 'temperature'),
         do = str_detect(variable, 'oxygen')) |> 
  summarise(sum(tw), sum(do))

model_meta |> 
  group_by(variable) |> 
  summarise(n())

# model classes by variable
model_meta |> 
  filter(str_detect(variable, 'temperature')) |> 
  group_by(model_type) |> 
  summarise(n())

model_meta |> 
  filter(str_detect(variable, 'oxygen')) |> 
  group_by(model_type) |> 
  summarise(n())

# use AT as a covariate?
model_meta |> 
  select(model_id, NOAA_var, variable) |>
  mutate(tw = str_detect(variable, 'temperature'),
         do = str_detect(variable, 'oxygen')) |> 
  filter(str_detect(NOAA_var, 'air_temp')) |>
  summarise(sum(tw), sum(do))

# types of uncertainty represented
# Number of models that contain each type
model_meta |>
  mutate(tw = str_detect(variable, 'temperature'))  |> 
  filter(tw == T) |> 
  summarise(across(contains('unc'), ~ sum(.x, na.rm = T)))

# How many sources are represented in each model?
model_meta |>
  mutate(tw = str_detect(variable, 'temperature'))  |> 
  filter(tw == T) |> 
  select(model_id, contains('unc_')) |> 
  mutate(unc_n = rowSums(pick(where(is.numeric)))) |> 
  group_by(unc_n) |> 
  summarise(n = n())

# Scores database summary -------------------------------------------------
# total forecasts - distinct model/site/var/refdate combos
distinct_forecasts <- arrow::open_dataset("./scores_v2") |> 
  distinct(model_id, site_id, variable, reference_datetime) |> 
  collect()

# variable forecasts
distinct_forecasts |> 
  group_by(variable ) |>
  summarise(n = n()) |> 
  mutate(percent = 100*(n/nrow(distinct_forecasts)))
